\begin{thebibliography}{99}

\bibitem{clinical_pd}
Greenland J C, Barker R A. The differential diagnosis of Parkinson's disease[M]// Stoker T B, Greenland J C, editors. Parkinson's Disease: Pathogenesis and Clinical Aspects. Brisbane: Codon Publications, 2018.

\bibitem{little2009}
Little M A, McSharry P E, Hunter E J, Spielman J, Ramig L O. Suitability of dysphonia measurements for telemonitoring of Parkinson's disease[J]. IEEE Transactions on Biomedical Engineering, 2009, 56(4): 1015--1022.

\bibitem{tsanas2010}
Tsanas A, Little M A, McSharry P E, Ramig L O. Accurate telemonitoring of Parkinson's disease progression by noninvasive speech tests[J]. IEEE Transactions on Biomedical Engineering, 2010, 57(4): 884--893.

\bibitem{dataset1}
Sakar B E, Isenkul M E, Sakar C O, Sertbas A, Gurgen F, Delil S, Apaydin H, Kursun O. Collection and analysis of a Parkinson speech dataset with multiple types of sound recordings[J]. IEEE Journal of Biomedical and Health Informatics, 2013, 17(4): 828--834.

\bibitem{dataset2}
Naranjo L, Perez C J, Campos-Roca Y, Martin J. Addressing voice recording replications for Parkinson's disease detection[J]. Expert Systems with Applications, 2016, 46: 286--292.

\bibitem{naranjo2017}
Naranjo L, Perez C J, Martin J, Campos-Roca Y. A two-stage variable selection and classification approach for Parkinson's disease detection by using voice recording replications[J]. Computer Methods and Programs in Biomedicine, 2017, 142: 147--156.

\bibitem{svm}
Cortes C, Vapnik V. Support-vector networks[J]. Machine Learning, 1995, 20(3): 273--297.

\bibitem{breiman}
Breiman L. Random forests[J]. Machine Learning, 2001, 45(1): 5--32.

\bibitem{sklearn}
Pedregosa F, Varoquaux G, Gramfort A, Michel V, Thirion B, Grisel O, Blondel M, et al. Scikit-learn: Machine learning in Python[J]. Journal of Machine Learning Research, 2011, 12: 2825--2830.

\bibitem{xgboost}
Chen T, Guestrin C. XGBoost: A scalable tree boosting system[C]// Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. 2016: 785--794.

\bibitem{shap}
Lundberg S M, Lee S I. A unified approach to interpreting model predictions[C]// Advances in Neural Information Processing Systems. 2017, 30: 4765--4774.

\bibitem{benjamini}
Benjamini Y, Hochberg Y. Controlling the false discovery rate: a practical and powerful approach to multiple testing[J]. Journal of the Royal Statistical Society: Series B, 1995, 57(1): 289--300.

\bibitem{lasso}
Tibshirani R. Regression shrinkage and selection via the lasso[J]. Journal of the Royal Statistical Society: Series B, 1996, 58(1): 267--288.

\bibitem{silhouette}
Rousseeuw P J. Silhouettes: A graphical aid to the interpretation and validation of cluster analysis[J]. Journal of Computational and Applied Mathematics, 1987, 20: 53--65.

\bibitem{calinski}
Calinski T, Harabasz J. A dendrite method for cluster analysis[J]. Communications in Statistics, 1974, 3(1): 1--27.

\bibitem{davies}
Davies D L, Bouldin D W. A cluster separation measure[J]. IEEE Transactions on Pattern Analysis and Machine Intelligence, 1979, PAMI-1(2): 224--227.

\bibitem{ari}
Hubert L, Arabie P. Comparing partitions[J]. Journal of Classification, 1985, 2: 193--218.

\end{thebibliography}
